\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname Team 24}

\date{Jan.29, 2025}

%\input{../Comments}
%\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo.

\section{Demo Plans}

We will be demonstrating the minimal working product of UNO-Flip. This includes demonstrating that our software can execute the game rules correctly, AI can be interacted like another player, as well as the multiplayer functionality that runs the game on at least two different machines which divide the game into user and AI modes.

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 7\\
Mingyang Xu& 7\\
Jianhao Wei & 7\\
Andy Liang & 2\\
Kevin Ishak & 5\\
Zain-Alabedeen Garada & 5\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 0\\
Mingyang Xu & 0\\
Jianhao Wei & 0\\
Andy Liang & 0\\
Kevin Ishak & 0\\
Zain-Alabedeen Garada & 0\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended over the time
period of interest.  This number should be determined from the lecture issues in
the team's repo.  The first entry in the table should be the total number of
lectures since the beginning of the term.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Mingyang Xu & 2\\
Jianhao Wei & 2\\
Andy Liang & 0\\
Kevin Ishak & 1\\
Zain-Alabedeen Garada & 0\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the lecture attendance can be provided here.}

\section{TA Document Discussion Attendance}

\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Mingyang Xu & 1\\
Jianhao Wei & 1\\
Andy Liang & 1\\
Kevin Ishak & 1\\
Zain-Alabedeen Garada & 1\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the attendance can be provided here.}

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 46 & 100\% \\
Mingyang Xu & 10 & 21.739\% \\
Jianhao Wei & 24 & 52.174\% \\
Andy Liang & 1 & 2.173\% \\
Kevin Ishak & 7 & 15.217\% \\
Zain-Alabedeen Garada & 4 & 8.696\% \\
\bottomrule
\end{tabular}
\end{table}

\wss{A portion of commits is for documents committed by one person with changes authored by multiple people.}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Mingyang Xu & 8 & 13 \\
Jianhao Wei & 13 & 25 \\
Andy Liang & 0 & 0 \\
Kevin Ishak & 1 & 10 \\
Zain-Alabedeen Garada & 0 & 8 \\
\bottomrule
\end{tabular}
\end{table}

\wss{Issues are usually generated to assign work and document meetings. It might not be a good indicator of the amount of work done.}


\section{CICD}

\wss{Say how CICD is used in your project}

\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.}

We will determine the share of work by the commits and issues each team members authored or assigned to determine if each member does a fair share of work. For testing our software, we will develop benchmarks during the period between Rev0 and VnV plan to testing our software by standard. We will also start to develop extra metrics for extra we chose for this project during that period.

\end{document}